---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "pdf/",
  out.width = "100%"
)
```

# Testing of cheatsheet components


This file is a rough checker of the cheatsheet, just to ensure
that code chunks are working as expected. 

It's running on a local computer with vigicaen up to date.
You might not be able to reproduce it as is.
```{r}
library(vigicaen)
```


```{r paths}
path_main  <- '/your/path/to/vigibase/main/'
path_sub   <- '/your/path/to/vigibase/sub/'
path_who   <- '/your/path/to/vigibase/who/'
path_meddra <-'/your/path/to/meddra/'

path_main  <- 'C:/Data/vigibase_2024_sep/main/'
path_sub   <- 'C:/Data/vigibase_2024_sep/sub/'
path_who   <- 'C:/Data/vigibase_2024_sep//who/'
path_meddra <-'C:/Data/Nextcloud/Database/meddra_27_1/MedAscii/'
```


## Load and assign tables

```{r}
demo <- dt_parquet(path_main, 'demo')
drug <- dt_parquet(path_main, 'drug')
adr <- dt_parquet(path_main, 'adr', in_memory = FALSE)
link <- dt_parquet(path_main, 'link', in_memory = FALSE)
mp <- dt_parquet(path_who, 'mp')
thg <- dt_parquet(path_who, 'thg')
meddra <- dt_parquet(path_meddra, 
'meddra_hierarchy')
smq_list <- dt_parquet(path_meddra, 'smq_list')
smq_content <- dt_parquet(path_meddra, 
'smq_content')
```

## Set up dictionary

```{r}
d_sel <-
  list(analgesics = c('paracetamol', 'tramadol'))
a_sel <-
  list(hepatitis = c('Hepatitis'))

smq_sel <-
list(ihd = c('Ischaemic heart disease (SMQ)'))

atc_sel <- list(cardiac_drugs = c('C01'))

a_sel_many <-
list(analgesics = c('paracetamol', 'tramadol'),
nivolumab = 'nivolumab',
ici = c('nivolumab', 'ipilimumab'))
```


## Collect IFs

```{r}
d_drecno <- get_drecno(d_sel , mp)

d_drecno_atc <- get_atc_code(atc_sel, mp, thg)

a_llt <- get_llt_soc(a_sel, term_level = 'pt', meddra)

a_llt_smq <- get_llt_smq(smq_sel, smq_list = smq_list, smq_content = smq_content)
```

## Plot graph

```{r}
vigi_routine(
demo, drug, adr, link,
d_code = d_drecno,
a_code = a_llt,
case_tto = 50,
vigibase_version = 'Sep 2024')

vigi_routine(
demo, drug, adr, link,
d_code = d_drecno,
a_code = a_llt,
case_tto = 50,
vigibase_version = 'Sep 2024',
export_to = 'graph.svg')
```

## Add drug & adr columns

```{r}
demo <-
add_drug(demo, d_drecno, drug_data = drug)

demo <-
add_drug(demo, d_drecno_atc, drug_data = drug)

demo <-
add_adr(demo, a_llt, adr_data = adr)
```
### Check data management

```{r}
check_dm(demo, c('analgesics', 'hepatitis'))
```
## Disproportionality

```{r}
compute_dispro(
demo, 'hepatitis', 'analgesics')

mod <- glm(hepatitis ~ analgesics + AgeGroup + 
Gender, family = 'binomial', data = demo)
summary(mod)$coefficients |> 
compute_or_mod(
estimate = Estimate, std_er = Std..Error
)
```

```{r}
tb_subset(path_main, 
   paste0(path_main, 'subset'),  
   subset_var = 'age',
   sv_selection = 7)

```

## Description

```{r}
desc_facvar(demo, vf = c('hepatitis', 'Gender'))

# demo <- dplyr::mutate(demo, date = lubridate::year(lubridate::ymd(FirstDateDatabase)))

# desc_cont(demo, vc = 'date') # irrelevant

```
### Link

```{r}
link <-
  add_drug(link, d_drecno, drug_data = drug) |>
  add_adr(a_llt, adr_data = adr)

desc_tto(link, 'analgesics',
  'hepatitis')


ttos <- extract_tto(link,
  'analgesics',
  'hepatitis')
hist(ttos$tto_max)

desc_dch(link |> dplyr::collect() |> data.table::as.data.table(),
  'analgesics',
  'hepatitis')

desc_rch(link |> dplyr::collect() |> data.table::as.data.table(), demo, 'analgesics', 'hepatitis')
```
### Adr

```{r}
adr <-
  add_drug(adr, d_drecno, drug_data = drug) |>
  add_adr(a_llt, adr_data = adr)

desc_outcome(adr |> dplyr::collect() |> data.table::as.data.table(), 'analgesics', 'hepatitis')
```

### Screen drugs & adrs

```{r}
screen_drug(drug, mp, 0.10)
screen_adr(adr, meddra, 'hlgt', 0.10)

```

